\TheTitle

### 2017-07-05 paper/lineval.tex
Placing related works back
The original related works section was fine, putting that back in
directly.
User Study: rename methodology -> Controlled User Study
Most of the methodology

%% Table Support
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{multirow}

@@

\section{Methodology}
\label{sec:methodology}

>>>>

%% Table Support
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{tabulary}

@@

\input{relatedwork.tex}

\section{Controlled User Study}
\label{sec:study}

We use a controlled mixed-methods users study in order to evaluate the
ability for the DAG to provide users with a conceptual image of how a
commit is integrated into a project, to compare the DAG and \mt models,
and determine which model the users preferred.

In this section, we describe the methods used to for designing and
implementing the user study.

\subsection{Questions and Tasks}
\label{sub:questions}

\begin{table*}[htpb]
  \centering
  \caption{Conceptual Tasks }
  \label{tab:conceptual_tasks}
  \begin{tabulary}{0.9\textwidth}{LL}
    \toprule
    Task & Description\\
    \midrule
    T1 & Draw a diagram showing how this commit was merged into the master branch, along with any other related commits\\
    T2 & How many individual commits are related to this commit?\\
    T3 & How many merges are involved with merging this commit into the master branch?\\
    \bottomrule
  \end{tabulary}
\end{table*}

\begin{table}[htpb]
  \centering
  \caption{Summarization Tasks}
  \label{tab:summarization_tasks}
  \begin{tabulary}{\linewidth}{LLL}
    \toprule
    Task Set   & Task & Description\\\midrule
    Merge      & T4   & What is the series of merges involved with merging this
    commit?\\
               & T5   & What other commits are merged?\\
    Authorship & T6   & How many authors are involved?\\
               & T7   & Who contributed the most changes?\\
    Files      & T8   & How many files were modified?\\
               & T9   & Which file had the most changes?\\
    Modules    & T10  & Which modules does this merge tree involve?\\
    \bottomrule
  \end{tabulary}
\end{table}

The questions and tasks are broken down into four groups. The first two
groups are purely quantitative in nature; we begin with conceptual tasks
to understand whether the DAG is capable of providing users with an
understanding of how a commit is merged into the master branch, and
other commits that it is merged with. We continue with summarization
tasks, to quantitatively understand if the \mt model makes a difference
in summarization tasks.

The third task set is purely qualitative, to gain better understanding
of whether participants preferred working with the \mt model in \tool,
or working with the DAG in Gitk, and what aspects they preferred from
each tool. The final group of questions is simply to gain a better
understanding of the demographic of our participants.

\textbf{Conceptual Tasks}

The participants were allowed to use Gitk or the git command line tools
to perform these tasks. These tasks are asked in the specified order,
allowing tabularr to first, create a conceptual understanding of the
commits and merges that will be involved with the rest of the tasks that
follow.tabularmay then use their diagrams to answer T2 and T3. We do not
collect metrics from \tool for the conceptual tasks, opting instead to
determine if the DAG is sufficient for understanding how a commit is
integrated. \tool uses the \mt model show a tree visualization of how
commits are merged, until the commit reaches the master branch.
Table~\ref{tab:conceptual_tasks} shows the conceptual tasks.

We provide the participant with 10 minutes per commit to complete the
first task. The answers to the two other questions in this section are
drawn from the answer in the first task.

\textbf{Summarization Tasks}

The summarization tasks (Table~\ref{tab:summarization_tasks}) are
grouped into task sets by theme. The tasks within the task set are
shuffled, and the task sets are shuffled, to ensure that similar
questions are together, but not in the same order, and to ensure that
the themes are in randomized order between participants. The order of
the commits is shuffled, as well. The order of the tool is randomized,
choosing to start with either \tool or Gitk, to ensure that we do not
place a bias on one tool through the experiment.

As understanding where the merge begins and ends is vital to answering
the other question, the merge task set will always be the first task set
presented; however, the questions will still be re-ordered within the
task set.

\textbf{User Opinion and Profile}

Finally, we ask the user for their opinions on the tools and for some
information about their level of experience with git. This portion of
the study is qualitative and does not rely on either of the tool,
instead attempting to determine which model provided the user with a
better experience.

We do not shuffle the questions in this set of questions, as this should
not have an impact on the opinions of the participant at this point.
These questions are designed to provide us with a better understanding
of preference, and insight on why, the participant had that preference.

We ask the following questions in this order;

\begin{enumerate}
  \item Given these tasks again, which tool would you prefer to use?
  \item Which aspects of each tool did you like and why?
  \item How long have you used git?
  \item If you have used git, for what kind of projects? (personal,
    school courses, professional?)
  \item If you have used git, how many commits, files, and contributors
    were involved with the largest repository you have worked with?
\end{enumerate}

The last three questions in this section are aimed at getting a better
understanding of the demographic of our participants.

\textbf{Procedure}

For each participant, we run a simple python script to generate the
script for the study, eliminating the possibility of bias from us. The
script randomizes the order of the tools, the order of the commits, the
order of the task sets, and the order of the tasks within each task set,
where appropriate.

\subsection{Commit Selection}
\label{sub:commit_selection}

We chose two commits for use in the study. The order that the commits
are presented is randomized between participants, but the order is kept
consistent through the tasks described in the next subsection.

We use the \tool database, containing commits and merge-tree information
from April 16th 2005 to October 14th, 2014, which corresponds to being
between Linux release 2.6.12-rc3 and Linux 3.17-rc1. \evan{Cite the
  database even more?} We chose the commits based on tree sizes. We
found that a majority of the trees contain at most seven inner commits,
while more than 25\% of the trees contain a single commit. 75\% of the
tree contained up to 51 inner commits and merges, and finally the
largest tree contained 7217 nodes. We chose to work with the trees in
the first and second quartile, as merge trees of sizes between one and
seven, not including the merge into the master branch, make up the
majority of the trees in the database.

From here, we selected one tree from the trees of a single commit at
random. Selecting a commit from that tree is trivial, as there is only
one to choose.

We selected one tree of size seven at random from all trees of size
seven. We placed a restriction the trees, the selected tree must include
at least one internal merge to increase the complexity of the trees
tested. After randomly selecting a tree, we chose in internal commit at
random, using the \verb|random.choice| function in python 3.6.1.

Using this technique, we selected commit
\emph{a3c1239eb59c0a907f8be5587d42e950f44543f8} from the tree containing
a single node (Figure~\ref{fig:commit_1}), which we will refer to as
\comA, and commit \emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, from
the tree containing seven nodes (Figure~\ref{fig:commit_2}), which we
will refer to as \comB.

\begin{figure}[bpt]
  \centering
  \includegraphics[width=0.08\linewidth]{figures/commits/1-commit.pdf}
  \caption{The first merge tree used in the user study, a merge tree
    containing a single commit}
  \label{fig:commit_1}
\end{figure}

\begin{figure}[bpt]
  \centering
  \includegraphics[width=0.5\linewidth]{figures/commits/7-commits.pdf}
  \caption{The second merge tree used in the user study, a merge tree
    containing seven commits}
  \label{fig:commit_2}
\end{figure}
